Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-07-01 paper/ms.tex
update manuscript

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Spot-induced stellar variability is the dominant signal.  Dashed
    lines show the five transits observed by TESS.  {\it Bottom}:
    Zoomed windows of individual transits.  Red points are manually
    identified stellar flares.
		\label{fig:rawzoom}
	}
\end{figure*}

>>>>

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Spot-induced stellar variability is the dominant signal; flares are
    shown with gray crosses.  Dashed
    lines indicate the five transits observed by TESS.  {\it Bottom}:
    Zoomed windows of individual transits.
    Gray lines are the best-fit transit model, which includes a local
    quadratic trend in each transit window.
		\label{fig:rawzoom}
	}
\end{figure*}
